### 2017-11-22 manuscript.rmd
moved gene occupancy to supplementary info

@@

####Phylogenetic signal in the character data
```{r phylosig_binaries_declare, echo=F, message=F, warning=F, include=F}
binaries_phylosig = multiPhylosignal(as.matrix(cdata[,c(2,5:8)]), ultratree)
names(binaries_phylosig)<-c("K","PICvar obs","PICvar rnd","P-value","Z-score")
```

#####Phylogenetic signal in Binary Traits
```{r phylosig_binaries, results='asis',echo=F, message=F, warning=F}
 # make it xtable
xtable_PS<-xtable(binaries_phylosig,auto=TRUE)
print(xtable_PS,comment=F)

```
#####Library assembly summary

```
### Software versions

>>>>

####£Agalma analysis

![60% gene occupancy matrix for 41 species across 1,071 genes. Genes and species are sorted by sampling, the best sampled shown in the upper left.](supplementary_info/gene_occupancy.png)

```
The assembly summary statistics for all included taxa, showing mean insert size, and the percentage of reads kept after pipeline steps.

@@

#####Phylogenetic signal in Binary Traits
```{r phylosig_binaries, results='asis',echo=F, message=F, warning=F}
 # make it xtable
binaries_phylosig = multiPhylosignal(as.matrix(cdata[,c(2,5:8)]), ultratree)
names(binaries_phylosig)<-c("K","PICvar obs","PICvar rnd","P-value","Z-score")
xtable_PS<-xtable(binaries_phylosig,auto=TRUE)
print(xtable_PS,comment=F)

```
Supplementary table x. Phylogenetic signal in the binary traits, including Blomberg's K statistic, the mean observed PIC variance, the random variance of PICs, p-value of the comparison of observed and random variance, and the z-score.

### Software versions
